---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
#Packages
```{r setup, include=FALSE}
library(haven)
library(foreign)
library(rio)
library(survey)
library(nnet)
library(ggplot2)
library(describer)
library(tidyverse)
library(psych)
library(MASS)
library(Hmisc)
library(reshape2)
library(margins)
library(stargazer)
library(mediation)
library(summarytools)
library(sjPlot)
library(dplyr)
```

#Commit containing full submission
## Code for reading in the dataset and/or processing the data
```{r, echo=TRUE}
setwd("\\Users\\ferre\\Desktop")
data <- read.csv("activity.csv")
data
```

## Histogram of the total number of steps taken each day
```{r}
hist1 <- data %>%
  group_by(date) %>% 
  summarise(steps=sum(steps))
hist1
histogram(hist1$steps)
```

## Mean and median number of steps taken each day
```{r}
hist2 <- data %>%
  group_by(date) %>% 
  summarise(mean = mean(steps), median=median(steps), steps=sum(steps))
hist2
```

## Time series plot of the average number of steps taken
```{r}
ggplot(hist2, aes(x=date, y=(steps), group = 1, na.rm = TRUE)) +
  geom_point() +
  geom_line() +
  xlab("Dates") +
  theme(axis.text.x=element_text(angle=60, hjust=1))

```

## The 5-minute interval that, on average, contains the maximum number of steps
```{r}
agginterval <- aggregate(data$steps ~ data$interval, FUN=sum)
filter(agginterval, agginterval$`data$steps`== max(agginterval$`data$steps`))
```

## Code to describe and show a strategy for imputing missing data
```{r}
table(is.na(data$steps))
```

## Histogram of the total number of steps taken each day after missing values are imputed
```{r}
histogram(data$steps)
```

## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
#I don't have an ideia how to do it.
```

